---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FAVAR

<!-- badges: start -->
<!-- badges: end -->

The goal of FAVAR is to estimate a FAVAR model by Bernanke et al. (2005).

## Installation

You can install the package FAVAR from CRAN:
```{r, eval=FALSE}
install.packages('FAVAR')
```



You can install the development version of FAVAR from [GitHub](https://github.com/common2016/FAVAR) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("common2016/FAVAR")
```

## Example

This is a basic example which shows you how to estimate a FAVAR model:

```{r example}
library(FAVAR)
## basic example code
data('regdata')
fit <- FAVAR(Y = regdata[,c("Inflation","Unemployment","Fed_funds")],
             X = regdata[,1:115], slowcode = slowcode,fctmethod = 'BBE',
             factorprior = list(b0 = 0, vb0 = NULL, c0 = 0.01, d0 = 0.01), 
             varprior = list(b0 = 0,vb0 = 10, nu0 = 0, s0 = 0),
             nrep = 500, nburn = 100, K = 2, plag = 2)
# print FAVAR estimation results
summary(fit,xvar = c(3,5))
# plot impulse response figure
library(patchwork)
ans <- irf(fit,resvar = c(2,9,10), tcode = tcode, nhor = 21, showplot = T)
```


## Reference


- Bernanke, B.S., J. Boivin and P. Eliasz, Measuring the Effects of Monetary Policy: A Factor-Augmented Vector Autoregressive (FAVAR) Approach. Quarterly Journal of Economics, 2005. 120(1): p. 387-422.

